\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingNoLink}[2]{\ProjectNoLink{#1}
\descript{#2}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

\newcommand{\projectHeadingWithDateNoLink}[3]{\ProjectNoLink{#1}
\descript{#2 | #3}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Alexander Worrall}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{TODO.com}
% vs how you want it to show up. If it's the same you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{https://TODO.com}
\newcommand{\yourEmail}{a.worrall2512@googlemail.com}
\newcommand{\yourPhone}{+447455079759}
\newcommand{\githubUserName}{ayorkshireworrall}
\newcommand{\linkedInUserName}{Alexander Worrall}
\newcommand{\linkedInUrl}{https://www.linkedin.com/mwlite/in/alexander-worrall-51b1881a5}

% An alternate profile section 
% \alignProfileTable
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%     \ralewayBold{\href{\yourWebsiteLink}{\Large \yourName}} & 
%     Email : \href{mailto:\yourEmail}{\yourEmail}
%     \\
%     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
%     Mobile : \yourPhone
%     \\
%     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsiteLink}{\yourWebsite}
%     \\
% \end{tabular*}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{1pt}
    \small \href{mailto:\yourEmail}{\underline{\yourEmail}}  $|$  \yourPhone $|$ 
    \href{\linkedInUrl}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}} 
    % $|$ \href{\yourWebsiteLink}{\underline{\yourWebsite}}
\end{center}

%--------------------------------------------------------------
%     Intro
%--------------------------------------------------------------
\projectHeadingNoLink{}{}
\par \noindent I am a software developer who specialises in Java web applications using Spring. I have a passion for technologies that provide opportunities for continuous learning. In addition to my expertise in backend Java code, I have experience working with hyperscalers, building and maintaining efficient build pipelines, and developing user interfaces with various frontend frameworks. I am always eager to take on new challenges and expand my skillset in software development.
\sectionsep

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Put school first and degree second if your school is reputable
\educationHeading{Durham University}{Undergraduate Mathematics (BSc. Honours)}{2:1}{Jun 2016}

\educationHeading{Ripon Grammar School}{A levels: Maths, Further Maths, Physics, History}{A*AAA}{Jul 2013}
\sectionsep

%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}
\resumeHeading{Deloitte SAP+}{Senior Consultant}{London}{Oct 2020- Present}
\par
Worked on projects for high profile public sector organisations engaging the clients on a daily basis. Responsible for educating and supporting junior team members alongside delivering new features for clients. Contributed to codebases, set up and maintained infrastructure and CI/CD pipelines for various projects.
\sectionsep

\resumeHeading{Keytree}{Graduate Software Engineer}{London}{Oct 2017- Oct 2020}
\par
Steep learning curve to gain an understanding of software and cloud technologies to become billable and work face to face with clients within 3 months of joining despite no prior software experience. 
\sectionsep

%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}

\projectHeadingWithDateNoLink{GLA OPS}{Java, Spring, AngularJS, Postgres, AWS, Selenium}{Jan 2021 - Jan 2023}
As a senior developer on an agile project, I worked on the Open Project System (OPS) - a grant application and distribution system for the Greater London Authority. It allows external applicants to apply for highly customizable programs, and tracks applicant projects with full auditing and version control. Automated payments are made based on approval criteria. The system is built to handle the nearly 3,000 organizations that have requested £10bn in funding, with £6bn already granted and paid through the application.\\
\sectionsep
  
\projectHeadingWithDateNoLink{NE OPS}{Java, Spring, AngularJS, Postgres, AWS, Selenium}{Oct 2020 - Jan 2021}
I set up a project application and grant management system using the GLA OPS open source code for a smaller client, the North of Tyne Combined Authority. This was a solo project where I set up AWS infrastructure, created a deployment pipeline, and configured the code to meet the client's branding and business requirements, including making necessary code changes.
\sectionsep

\projectHeadingWithDateNoLink{Plan Zheroes}{NodeJS, ReactJS, Postgres, AWS, Kubernetes}{Apr 2020-Oct 2020}
I worked on a pro bono legacy project to establish a network for volunteers to distribute excess food from businesses to charities in need. I migrated the project from broken infrastructure to a Kubernetes cluster and configured a new build pipeline. I also conducted a security audit of vulnerable APIs and fixed defects in the front-end ReactJS and back-end NodeJS code.
\sectionsep

\projectHeadingWithDateNoLink{GRP2}{Java, Liferay, OSGI, MySQL, ReactJS, Selenium}{Jan 2018-Apr 2020}
I contributed to a custom Liferay content management system for a global UK-based car manufacturer. The application served as a single sign-on point for employees and targeted specific content to individual user types based on the client's complex business structure. I implemented automated e2e regression testing using Selenium, managed OSGI dependencies, and built an automated process to provision sites, organizations, and users based on a CSV input feed.
\sectionsep

% Example using bullets and dates 
% \projectHeadingWithDate{Hogwart\textquotesingle{}s Library Management System}{https://github.com/Aarif123456/hogwartslibrary}{PHP, JavaScript, HTML, CSS, MySQL}{Aug 2019}
% \begin{bullets}
    % \item A full-stack library management system, where users can manage books and holds on their accounts. Users can search the library\textquotesingle{}s catalogue, which has every book mentioned in the Harry Potter series. The system distinguishes between 4 users. For examples, librarians who can also check or return books on behalf of users.\\
% \end{bullets}
% \sectionsep
  

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills \& Qualifications}
\begin{skillList}
    \singleItem{Proficient Languages / Frameworks:}{Java, SQL, Spring, JavaScript, TypeScript, AngularJS, ReactJS, HTML/CSS}
    \\
    \singleItem{Hobby Languages / Frameworks:}{NodeJS, Python, Django, Rust}
    \\
    \singleItem{Technology:}{Teamcity, Git, AWS, GCP, Docker, Postgres, Kubernetes}
    \\
    \singleItem{Qualifications}{Google Cloud Associate Cloud Engineer}
\end{skillList}

% A more concise alternate 
% \begin{skillList}
%     \doubleItem{Languages:}{Java, C++, Python, C\#, PHP, Prolog, Bash, C, Racket}%
%     {Databases:}{SQL, MongoDB, Neo4j, DynamoDB}
%     \\
%     \doubleItem{Web Development:}{JavaScript, TypeScript, React, HTML/CSS}
%     {Technology:}{Git, AWS, GCP, Azure, Docker, \LaTeX}%
% \end{skillList}
\end{document}